---
title: "premierLeague"
author: "Kolawole Gabriel,Agaba Isaac"
date: "5 May 2016"
output: html_document
---



## Current Season

```{r se2015_2016}
library()
# se20152016  <- read.csv("~/Documents/Materials/2nd Semester Year1/2. Data Mining/project/dataset/2015-2016.csv")
# se20142015  <- read.csv("~/Documents/Materials/2nd Semester Year1/2. Data Mining/project/dataset/2014-2015.csv")
setwd("C:/Users/akaiz/Documents/data mining/data")
se20152016  <- read.csv("dataset/2015-2016.csv")
se20142015  <- read.csv("dataset/2014-2015.csv")

se20142015['bookings_y'] <- se20142015$HY + se20142015$AY 
se20142015['bookings_r'] <- se20142015$HR + se20142015$AR 

```

## Referees

```{r pressure, echo=FALSE}
library(plotly)
refMatchFreq16 <- as.data.frame(ftable(se20152016$Referee)) 
refMatchFreq15 <- as.data.frame(ftable(se20142015$Referee)) 
p1 <- plot_ly(
  x = refMatchFreq15$Var1,
  y = refMatchFreq15$Freq,
  name = "2015-2016 Season officiation Stat",
  type = "bar"
)
p2 <- plot_ly(
  x = refMatchFreq16$Var1,
  y = refMatchFreq16$Freq,
  name = "2014-2015 Season officiation Stat",
  type = "bar"
)

displayRefMatchBar <- function(obj){
    p <- layout(obj,              
      xaxis = list(           
          title = "Referee",  
          showgrid = T        
      ),
      yaxis = list(           
          title = "Number of Matches"   
      )
  )
    return(p);
}
# 
# displayRefMatchBar(p1)
# displayRefMatchBar(p2)
```

## 2014-2014 Season Officiating Stat
```{r statA}
displayRefMatchBar(p2)
```

## 2015-2016 Season Officiating Stat
```{r statB}
displayRefMatchBar(p1)
```

Next we are going to analyze the how players are booked in various matches during the two seasons, first let us figure out the match where most booking was done:

```{r matchbookings}

```

## Team Winning Stat 2015/2016
```{r fulltimescore}
plotPie <- function(data,season){
  ds <- as.data.frame(table(data$FTR))
  return(
          plot_ly(ds, labels = Var1, values = Freq, type = "pie") %>%
          layout(title = paste("Fulltime Result distribution",season,"season",sep=" "))
  )
}
plotPie(se20152016,"2015/2016")
plotPie(se20142015,"2014/2015")
```

From this is evident that the home team wins most matches. With a slight difference in the 2015/2016 season where the competition was evidently tough, where a non top 4 team (e.g Leceiter) is coming from below to dominate the league and several other teams like this.

We can further query this, is winning a match a function of being the home team in a match
```{r doesHomeMatters}
doesFactorMatter <- function (dataset,factor){
  factorSubset = subset(dataset, FTR==factor)
  if(factor == 'H'){
    shots <- mean(factorSubset$HST)
  }else{
    shots <- mean(factorSubset$AST)
  }
  return(paste("The avarage shot at the goal when the", factor, "wins", shots, sep= " "))
}
doesFactorMatter(se20152016,'H')
doesFactorMatter(se20152016,'A')
doesFactorMatter(se20142015,'H')
doesFactorMatter(se20142015,'A')

```

Looking the mean of the goals on target we can see that the home team has more goals on target, this can be due to the intimadating presence of the fans of the home team which is a usual culture in the english football.

