---
title: "premier_league_2"
author: "Agaba isaac"
date: "May 9, 2016"
output: html_document
---

## Current Season

```{r se2015_2016}
  library(dplyr)
    library(tidyr)

setwd("C:/Users/akaiz/Documents/data mining/data")


se20062007  <- read.csv("dataset/2006-2007.csv")
se20072008  <- read.csv("dataset/2007-2008.csv")
se20082009  <- read.csv("dataset/2008-2009.csv")
se20092010  <- read.csv("dataset/2009-2010.csv")
se20102011  <- read.csv("dataset/2010-2011.csv")
se20112012  <- read.csv("dataset/2011-2012.csv")
se20132014  <- read.csv("dataset/2013-2014.csv")
se20142015  <- read.csv("dataset/2014-2015.csv")

  year1<-se20062007
  year2<-se20072008
  year3<-se20082009
  year4<-se20092010
  year5<-se20102011
  year6<-se20112012
  year7<-se20132014
  year8<-se20142015


```

## Referees

```{r pressure, echo=FALSE}

looper=function(team,table,title){
   point = 0
   galldif=0
  for (i in 1:nrow(table)) {
   
    if(table[i,]$HomeTeam==team |table[i,]$AwayTeam==team){
         # print(paste0(table[i,]$HomeTeam,"=======",table[i,]$AwayTeam,">",table[i,]$FTR))
      
        if(table[i,]$HomeTeam==team & table[i,]$FTR=="H" )
        {
          point=point+3
          galldif=galldif+(table[i,]$FTHG-table[i,]$FTAG)
             
          
        }
        else  if(table[i,]$HomeTeam!=team & table[i,]$FTR=="H" ){
           galldif=galldif-(table[i,]$FTHG-table[i,]$FTAG)
        }
      
      
      
      if(table[i,]$AwayTeam==team & table[i,]$FTR=="A" )
        {
          point=point+3
            
              galldif=galldif+(table[i,]$FTAG-table[i,]$FTHG)
          
      }
      else  if(table[i,]$AwayTeam!=team & table[i,]$FTR=="A" ){
           galldif=galldif-(table[i,]$FTAG-table[i,]$FTHG)
        }
      
      if(table[i,]$FTR=="D")
        {
          point=point+1
            
      }
       
      
      
      
    }

  }
   

      
        t=paste("rankings/ranking_",title,".csv")
        
      
      write(c(team,point,galldif), file = t, 3, append = TRUE, sep = ",")
  
}


table_generator = function(team,title)
{
  teams = unique(team$HomeTeam)
  
  t=paste("rankings/ranking_",title,".csv")
  write(c("team","points","GDF"), file = t, 3, append = TRUE, sep = ",")
for(t in teams)
{
 
  looper(t,team,title)
}

  
}



```

#Generating table from the table generator


```{r}
table_generator(se20062007,"se20062007")
table_generator(se20072008,"se20072008")
table_generator(se20082009,"se20082009")
table_generator(se20092010,"se20092010")

```
# Acess to the generated results sata
```{r}
se20062007_result   <- read.csv("rankings/ranking_ se20062007 .csv",header = TRUE)
se20062007_result<-arrange(se20062007_result,desc(points))

se20072008_result   <- read.csv("rankings/ranking_ se20072008 .csv",header = TRUE)
se20072008_result<-arrange(se20072008_result,desc(points))



```


## PREDICTOR GENERATOR

## PARAMETERS
1. Extract out the number of matches played by the teams in the past years and the result of the game   

2. use various table attributes to train our  database

3. Get the current position of both teams in the last year
4. Get the current position of both the teams in the current year before they meet 

   1. This will base on whether they are meeting in the first round or not
   
   
   
```{r}
team_overalldata_in_past_year<-function(team,year){
  
  param=c("HomeTeam","AwayTeam","FTHG","FTAG","FTR","Referee","HS","AS","HST","AST","HC","AC","HF","AF","HY","AY","HR","AR")
  data<-subset(year,HomeTeam==team|AwayTeam==team)[,param]
  return(data)
}
                              



twoteams_matches_in_ayear<-function(team1,team2,year){
  fn<-"twoteams.csv"

 if (file.exists(fn)) file.remove(fn)
# write(c("HomeTeam","AwayTeam","FTHG","FTAG","FTR","Referee","HS","AS","HST","AST","HC","AC","HF","AF","HY","AY","HR","AR"), file = fn, 18, append = TRUE, sep = ",")

   teamresults<-team_overalldata_in_past_year(team1,year)
   rownames(teamresults) <- NULL
   #write(teamresults,file = fn, 18, append = TRUE, sep = ",")
   write.table(teamresults,fn,sep = ",")
   
# for(i in 1:nrow(teamresults)){
#  
#    team<-teamresults[i,]
#    x<-team$HomeTeam
#  write(c(x,team$AwayTeam,team$FTHG,team$FTAG,team$FTR,team$Referee,team$HS,team$AS,team$HST,team$AST,team$HC,team$AC,team$HF,team$AF,team$HY,team$AY,team$HR,team$AR), file = fn, 18, append = TRUE, sep = ",") 
#    print(paste(x,team$AwayTeam))
#  }
  
  
}

twoteams_matches_in_ayear("Arsenal","c",year1)
team_overalldata_in_past_year("Arsenal",year1)
                                                  




```









